%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
% Author:
% Gabriel Féron <feron.gabriel@gmail.com>
%
% Many thanks to https://twitter.com/thefakeincabell
% for the free design advice!
%
% Forked from the awesome template from posquit0
% https://github.com/posquit0/Awesome-CV
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[10pt, a4paper]{awesome-cv}
\usepackage{lastpage}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-concrete}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{Gabriel}{Féron}
\position{Lead DevOps Engineer}
% \address{}

\mobile{(+49) 1517-283-1232}
\email{feron.gabriel@gmail.com}
\github{gferon}

\begin{document}
\raggedright

\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
{\today}
{/* Gabriel Féron · Curriculum Vitae */}
{Page \thepage /\pageref{LastPage}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventrytitle
	{\href{https://developer.here.com}{HERE Technologies}}
	{Berlin, Germany}

	\cventry
	{Lead DevOps Engineer}
	{since January 2019}
	{
		\begin{cvparagraph}
			Member of the Routing Team (+40 people) responsible for developing routing services (trip planning and directions), data processing pipelines as well as maintaining core libraries, \textbf{designing APIs} and fixing various issues.
		\end{cvparagraph}
		\begin{cvitems}
			\item {Designed, prototyped, developed and launched the \href{https://developer.here.com/documentation/large-matrix/api-reference-swagger.html}{Matrix Routing v8} service, \textbf{written in Rust}, as a team lead.
			            The service is designed as a set of \textbf{distributed micro-services in Kubernetes} using \textbf{Redis} as queue and cache storage.}
			\item {Currently responsible for \textbf{feature development and stability} of the \href{https://developer.here.com/documentation/large-matrix/api-reference-swagger.html}{Matrix Routing v8} service.}
			\item {Helped foster the \textbf{introduction of Rust} to the team, starting in 2018.}
			\item {Continuously pushed for \textbf{improving cross-role collaboration} to enable developers to \textbf{own their changes end to end}.}
			\item {Introduced \textbf{GitLab with CI/CD} to our team with minimal disruption to the existing developer work-flow.}
		\end{cvitems}
	}

	\vspace{2pt}
	\cventry
	{Senior DevOps Engineer}
	{from January 2017 to December 2018}
	{
		\begin{cvitems}
			\item {Responsible for the \textbf{testing strategy, deployment pipelines and functioning} of all the \textbf{high-traffic Routing services} used by hundreds of customers around the world.}
			\item {Introduced \textbf{infrastructure as code} in the team using \textbf{Terraform}.}
			\item {Active member of a cross-team effort to refactor and maintain the \textbf{CMake build-system} used to assemble hundreds of C++ components developed by location service teams (Rendering, Routing, Traffic, Navigation).}
			\item {Migrated the test libraries for \textbf{Robot Framework} used by the team from Python 2 to \textbf{Python 3}.}
			\item {Pushed for and setup \textbf{continuous deployment} (release processes \& pipelines) for the \href{https://developer.here.com/products/routing}{three main Routing services}.}
			\item {Designed and deployed a tool to help all teams share \textbf{Docker images}, propagate updates and re-use existing layers.}
			\item {Participated in the development of the current iteration of the CI system (\textbf{Gerrit} + \textbf{Jenkins}) used by all teams in HERE Berlin.}
		\end{cvitems}
	}
\end{cventries}

\begin{cventries}

	\cventrytitle
	{Global Leads Group}
	{Berlin, Germany}

	\cventry
	{Systems Engineer}
	{from November 2015 to September 2016}
	{
		\begin{cvitems}
			\item {Migrated all dedicated servers to AWS, dividing the hosting budget by 5 while improving resilience and scalability.}
			\item {Developed a custom continuous integration pipeline integrated with Jenkins, Slack and Bitbucket using Python and the Docker API.}
		\end{cvitems}
	}

\end{cventries}

\begin{cventries}

	\cventrytitle
	{\href{https://www.lepape.com}{Lepape}}
	{Paris, France}

	\cventry
	{Software Developer}
	{from August 2012 to November 2015}
	{
		\begin{cvitems}
			\item {Setup a new dedicated hosting platform to withstand sales traffic spikes as well as its monitoring, failure and recovery strategy.}
			\item {Setup logging persistence and monitoring dashboards with Elasticsearch, Logstash and Kibana.}
			\item {Improved performance of the Magento e-commerce website by optimizing the back-end's code and database queries.}
			\item {Developed a payment transactions and order processing API for the back-office.}
			\item {Designed and developed a product catalog application in Java and MongoDB managing every product sold in the company's stores.}
		\end{cvitems}
	}
\end{cventries}
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Projects}
\begin{cventries}
	\cventrytitle
	{Open-source contributions}
	{}

	\cventry
	{Fedora Project}
	{since January 2019}
	{
		\begin{cvitems}
			\item{\href{https://src.fedoraproject.org/rpms/cura}{Packager of Cura for Fedora Linux}, a 3D printer slicing software}
		\end{cvitems}
	}

	\cventry
	{GitHub}
	{since 2012}
	{
		\begin{cvitems}
			\item {\href{https://github.com/gferon/rustberrypi-playground}{Rust device drivers for some} RaspberryPi \href{https://github.com/gferon/am2320.rs}{peripherals} from Adafruit}
			\item {\href{https://github.com/mitsuhiko/redis-rs/pull/305}{Added support for TLS in the Rust redis client}}
			\item {\href{https://github.com/OpenAPITools/openapi-generator/pulls?q=is\%3Apr+author\%3Agferon+is\%3Aclosed}{Improvements to the Rust OpenAPI generator}}
			\item {Contributor to \href{https://github.com/heremaps/flatdata}{Flatdata, a fast read-only serialization \& deserialization library} open-sourced during my work at HERE}
		\end{cvitems}
	}
\end{cventries}
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Skills}
\begin{cvskills}
	\cvskill
	{Programming}
	{Rust, Python, Java}

	\cvskill
	{Operating systems}
	{Linux (Fedora \& Debian)}

	\cvskill
	{Infrastructure}
	{AWS, Docker, Kubernetes, Terraform, Ansible}

	\cvskill
	{Observability}
	{Prometheus, Grafana, Splunk, Elasticsearch, Kibana, Logstash}

	\cvskill
	{Build tools \& CI}
	{GitLab CI, Jenkins, Gerrit, GitHub, CMake, RPM}

	\cvskill
	{Languages}
	{French (\emph{Native}), English (\emph{Fluent}), German (\emph{Basic})}
\end{cvskills}

\newpage
\cvsection{Education}

\cvsubsection{Internships}

\begin{cventries}

	\cventrytitle
	{Alstom Transport}
	{Saint-Ouen, France}

	\cventry
	{Automated train supervision team}
	{from January 2012 to August 2012}
	{
		\begin{cvparagraph}
			Developed a WYSIWYG software in C++ 11 (Qt 4) to design \& run test-cases for parts of the train supervision system.
		\end{cvparagraph}
		\vspace{4pt}
	}

	\cventrytitle
	{RATP (Autonomous Parisian Transportation Administration)}
	{Saint-Denis, France}

	\cventry
	{Maintenance Department}
	{from February 2011 to August 2011}
	{
		\begin{cvparagraph}
			Developed a project management software to assist with regular planned escalator maintenance.
		\end{cvparagraph}
	}

\end{cventries}

\cvsubsection{Curriculum}

\begin{cventries}
	\cventrytitle
	{ECE Paris}
	{Paris, France}

	\cventry
	{Engineering Diploma (Masters) in Computer Science}
	{from September 2007 to June 2012}
	{
		\begin{cvparagraph}
			Studied software engineering \& electronic systems design.
		\end{cvparagraph}
		\vspace{4pt}
	}

	\cventrytitle
	{University of Oslo}
	{Oslo, Norway}

	\cventry
	{Erasmus Semester in Multimedia Networking}
	{from August 2011 to January 2012}
	{
		\begin{cvparagraph}
			Studied heterogeneous multi-core architectures and multimedia networking using network processor cards.
		\end{cvparagraph}
		\vspace{4pt}
	}

	\cventrytitle
	{Concordia University}
	{Montréal, Canada}

	\cventry
	{Semester abroad in Electrical Engineering}
	{from August 2009 to December 2009}
	{
		\begin{cvparagraph}
			Studied analog electronics circuit design and C++ development.
		\end{cvparagraph}
		\vspace{4pt}
	}

\end{cventries}

\cvsection{Personal}

\begin{cventries}
	\descriptionstyle{
		\begin{cvitems}
			\item {Road biking}
			\item {3D printing}
			\item {Scuba diving}
			\item {I pour my milk in the bowl before the cereal}
		\end{cvitems}
	}
\end{cventries}

\end{document}